### 2019-02-13 sections/relatedwork.tex
related work: session types

>>>>

\subsection{Session types}

Session types are a type discipline that can be used to check whether communicating programs conform to a certain protocol.
Session types are expressions in some process calculus that describe the input/output behavior of such programs.
Session types are useful for programming languages where modules communicate with each other via messages, like CSP, $\pi$-calculus, or Go, to name a few.
The only form of messages in \TOP are input events which drive execution, but modules do not communicate using messages.
Therefore, session types are not applicable to \TOP in the sense used in the literature.

Formal reasoning about \TOP programs is one of our future goals for \TOPHAT.
The ideas and techniques of session types could be useful for specifying that a list of inputs of a certain form leads to desired task values.
The details are a topic for future work.
